
\subsection{Primitive Data Types}

 Alas, the C++ standard does not define all data types needed within
 SAGA.  For that reason, we provide these types also in the \T{saga}
 namespace.  Although these types should usually map to the native
 types on the respective platform the SAGA application is running on,
 we can only guarantee portability when using the SAGA provided types.

 The types provided by SAGA are:

 \begin{mycode}[label=Primitive types in the saga namespace]
  namespace saga
  {
    typedef  ...   char_t;

    typedef  ...   int8_t;             
    typedef  ...   uint8_t;            

    typedef  ...   int16_t;            
    typedef  ...   uint16_t;           

    typedef  ...   int32_t;            
    typedef  ...   uint32_t;           

    typedef  ...   int64_t;            
    typedef  ...   uint64_t;           

    typedef  ...   intmax_t;      
    typedef  ...   uintmax_t;     

    typedef  ...   long_long_t;

    typedef  ...   size_t;
    typedef  ...   ssize_t;
    typedef  ...   off_t;
  
  } // namespace saga
 \end{mycode}

 Note that the |int64_t| and |unit64_t| are only defined on those
 platforms which support 64 bit integers.  How the individual types
 are defined is platform-dependent, and should not be relied upon.
 However, they will often be mapped to the respective Boost
 types.


\subsection{Boost, and C++/TR1}
 
 Our implementation relies heavily on Boost \cite{boost}.  Boost is
 an open source collection of state-of-the-art C++ libraries, is
 highly portable, and is actually thought to be the playground for
 upcoming versions of the C++ standard.  In fact, all Boost features
 visible on the surface of our SAGA implementation (i.e., visible to
 the user of SAGA), are features which can already be found in the
 'C++ Technical Recommendation 1' \cite{tr1}, a recent extension of the
 C++ standard.  However, if your compiler does not support the TR1
 extensions yet, Boost is required to use SAGA.  Please refer to the
 installation manual for details on Boost.

 \X{correct?}

